BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC

### 2019-11-13 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
change BACI rmd to use theme_black for black background argument

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Redbanded Rockfish" 
    region: "both odd year surveys"
    #region: "West Coast Vancouver Island"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.25
editor_options: 
  chunk_output_type: inline
---

@@

# Calculate climate vectors
```{r }
vocc_by_year <- lapply(start_years, function(start_time) {
  # try({
  #   vocc <- readRDS(paste0(
  #     "data/vocc-", ssid_string, "-", climate_string, "-",
  #     min_string, "to", max_string, "-", start_time, "-", delta_t_total, "-update.rds"
  #   ))
  # })

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        # theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        # theme = "black",
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_e",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc, 
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        # raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,  
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

@@

      vocc_plot <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

    vocc_plot <- plot_vocc(biomass,
        theme = "black",
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        #white_zero = FALSE,
        white_zero = TRUE,
        mid_fill = "black",
        high_fill = "#66C2A5", #"Steel Blue 4", "#3288BD", #
        low_fill = "#5E4FA2FF", #"Red",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "#66C2A5", #"3288BD", #"Steel Blue 4",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  fourth_root_power #sqrt # no_trans ##
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) #+ theme_black()

@@

    vocc_plot <- plot_vocc(biomass,
      theme = "black",
       coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        #max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) 
       # +
       #  theme_black()
       # 
    vocc_plot
  })
})

@@

       vocc_plot <- plot_vocc(biomass,
         theme = "black",
         coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))

>>>>

---
title: "BACI of `r paste(params$species)` biomass for `r paste(params$region)` VOCC"
author: "Philina English"
date: "`r Sys.Date()`"
output: html_document 
params: 
    species: "Pacific Cod" 
    #region: "both odd year surveys"
    region: "West Coast Vancouver Island"
    age: "mature"
    biomass_threshold: "50"
    climate: "temperature"
    threshold: 0.5
editor_options: 
  chunk_output_type: inline
---

@@

# Calculate climate vectors
```{r }
vocc_by_year <- lapply(start_years, function(start_time) {
  try({
    vocc <- readRDS(paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, "-update.rds"
    ))
  })

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_est_e",
        fill_label = paste(" DO change\n", start_time, 
          "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        # white_zero = TRUE,
        # high_fill = "Steel Blue 4",
        # low_fill = "Red 3",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc, 
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_e",
        fill_label = paste(" Temperature\n change\n", 
          start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min_temp, raster_max_temp),
        # white_zero = TRUE,
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

    if (climate == "temperature") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc, 
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "#9E0142",
        # mid_fill = NULL, #"#FFFEC9", #cream
        # high_fill = "#D53E4F",#"Steel Blue 4"
        # low_fill = "#5E4FA2",
        white_zero = TRUE,
        vec_col = "white",
        vec_alpha = 0.45,
        axis_lables = FALSE,
        transform_col =  sqrt #fourth_root_power
      ) + ggtitle(climate) #+ ggpubr::theme_transparent()# +  theme_black()
    }

    if (climate == "do") {
      vocc$diff <- vocc$units_per_decade / 10 * delta_t_total
      vocc_plot <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        #raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt# no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(" Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vocc,  
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(" DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 3",
        low_fill = "Red 2",
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = sqrt #no_trans
      ) + ggtitle("do")

@@

      vocc_plot <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("Temperature\n change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
      vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste("DO change\n", start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        na_colour = "gray",
        white_zero = TRUE,
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        na_colour = "gray",
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.65,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

@@

    vocc_plot <- plot_vocc(biomass,
        theme_black = TRUE,
        coast = TRUE,
        vec_aes = "distance",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "density_diff",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        # varidis_option = 
        #white_zero = FALSE,
        white_zero = TRUE,
        mid_fill = "black",
        high_fill = "#66C2A5", #"Steel Blue 4", "#3288BD", #
        low_fill = "#5E4FA2FF", #"Red",
        # high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        # low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"   
        na_colour = "#66C2A5", #"3288BD", #"Steel Blue 4",
        vec_col = "white",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col =  fourth_root_power #sqrt # no_trans ##
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) #+ theme_black()

@@

    vocc_plot <- plot_vocc(biomass,
      theme_black = TRUE,
       coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        #max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" )) 
       # +
       #  theme_black()
       # 
    vocc_plot
  })
})

@@

       vocc_plot <- plot_vocc(biomass,
         theme_black = TRUE,
         coast = TRUE,
        vec_aes = "distance",
        vec_col = "white",
        arrowhead_size = 0.01,
        vec_lwd_range = c(.7, 1),
        min_vec_plotted = input_cell_size*2,
        max_vec_plotted = max_vector,
        NA_label = ".",
        fill_col = "start_density",
        fill_label = paste("Biomass\n change (kg/ha)\n", 
            start_time, "to", start_time + delta_t_total, ""),
        raster_alpha = 1,
        viridis_option = "C",
        #raster_limits = c(raster_min, raster_max),
        #white_zero = TRUE,
        #high_fill = "#21908CFF", # "#E6F598" "#ABDDA4" "#66C2A5" "#3288BD" "#5E4FA2"
        #low_fill = "#FDE725FF", #"#FEE08B", # "#9E0142" "#D53E4F" "#F46D43" "#FDAE61" "#FEE08B"
        na_colour = "red",
        vec_alpha = 0.35,
        axis_lables = FALSE,
        transform_col = fourth_root_power # no_trans #
      ) + ggtitle(paste0(threshold, " units of ", climate, " change below ", 
        biomass_threshold, "% of peak predicted ", species, " biomass" ))
